### 2015-02-18 fundamentals/acros.tex
minor revisions
fixing spelling error and double CI definition in acros.tex
adding DRE acronym
lcoe should not be repeated
fixin some bib issues
the genius acronym should just encapsulate the acronym.

\newacronym{GENIUSv1}{GENIUS}{Global Evaluation of Nuclear Infrastructure 
Utilization Scenarios, Version 1}
\newacronym{GENIUSv2}{GENIUS}{Global Evaluation of Nuclear Infrastructure Utilization Scenarios, Version 2}

@@

\newacronym{ORION}{ORION}{O..}

@@

@@

>>>>

\newacronym{GENIUS}{GENIUS}{Global Evaluation of Nuclear Infrastructure Utilization Scenarios}
\newacronym{GENIUSv1}{GENIUSv1}{Global Evaluation of Nuclear Infrastructure Utilization Scenarios, Version 1}
\newacronym{GENIUSv2}{GENIUSv2}{Global Evaluation of Nuclear Infrastructure Utilization Scenarios, Version 2}

@@

\newacronym{ORION}{ORION}{ORION}

@@

\newacronym{MOX}{MOX}{Mixed Oxide}
\newacronym{UOX}{UOX}{Uranium Oxide}

@@

\newacronym{DRE}{DRE}{Dynamic Resource Exchange}
\newacronym{DESAE}{DESAE}{Dynamic Analysis of Nuclear Energy Systems Strategies}
\newacronym{MILP}{MILP}{Mixed-Integer Linear Program}
\newacronym{LP}{LP}{Linear Program}

### 2015-02-18 fundamentals/intro.tex
the genius acronym should just encapsulate the acronym.

\Cyclus emerged from a line of tools seeking to break this practice.  Its
precursor,
\gls{GENIUSv1}\cite{dunzik-gougar_global_2007,jain_transitioning_2006},
originated within \gls{INL} and sought to provide generic regional capability.
Based on lessons learned from Version 1, the \acrshort{GENIUSv2} Version
2\cite{oliver_studying_2009,huff_geniusv2_2009} simulator sought to provide more
generality and an extensible interface to facilitate collaboration.  The
\Cyclus project then improved upon the \acrshort{GENIUSv2} effort by
implementing increased modularity and encapsulation.  The result is a dynamic
simulator that treats both materials and facilities discretely, with an
architecture that permits multiple and variable levels of fidelity. The
simulator's agent-based framework for tracking the transformation and trade of
resources between autonomous regional and institutional entities with
customizable behavior and objectives is an innovation not pursued by any
existing fuel cycle simulator.

>>>>

\Cyclus emerged from a line of tools seeking to break this practice.  Its
precursor,
\gls{GENIUS} Version 1 \cite{dunzik-gougar_global_2007,jain_transitioning_2006},
originated within \gls{INL} and sought to provide generic regional capability.
Based on lessons learned from \gls{GENIUS} Version 1, the \gls{GENIUS} Version
2 \cite{oliver_studying_2009,huff_geniusv2_2009} simulator sought to provide more
generality and an extensible interface to facilitate collaboration.  The
\Cyclus project then improved upon the \gls{GENIUS} effort by
implementing increased modularity and encapsulation.  The result is a dynamic
simulator that treats both materials and facilities discretely, with an
architecture that permits multiple and variable levels of fidelity. The
simulator's agent-based framework for tracking the transformation and tradef
resources between autonomous regional and institutional entities with
customizable behavior and objectives is an innovation not pursued by any
existing fuel cycle simulator.
